---
title: "Mobile Analytics"
author: "Yuzi Liu"
date: "11/19/2018"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
library(aspace)
library(stargazer)
library(corrplot)
library(plyr)
library(knitr)
opts_chunk$set(echo = TRUE)
```

# Data Processing


```{r}
getwd()
mobile <- read.csv("Geo-Fence Analytics.csv", header = TRUE)
```
* 1a.	Create dummy variable imp_large for the large impression:
* 1b.	Create dummy variables cat_entertainment, cat_social and cat_tech for app categories:
* 1c.	Create dummy variable os_ios for iOS devices:

```{r}
mobile$imp_large <- ifelse(mobile$imp_size == "728x90", 1, 0)


mobile$cat_entertainment <- ifelse(mobile$app_topcat %in% c("IAB1","IAB1-6"), 1, 0)
mobile$cat_social <- ifelse(mobile$app_topcat == "IAB14", 1, 0)
mobile$cat_tech <- ifelse(mobile$app_topcat == "IAB19-6", 1, 0)

mobile$os_ios <- ifelse(mobile$device_os == "iOS", 1, 0)
```

* 1d.	Create variable distance using Harvesine formula to calculate the distance for a pair of latitude/longitude coordinates.
* 1e.	Create variable distance_squared by squaring variable distance
* 1f.	Create variable ln_app_review_vol by taking natural log of app_review_vol

```{r}
mobile$distance = 6371*acos(cos(as_radians(mobile$device_lat))*
                     cos(as_radians(mobile$geofence_lat))*cos(as_radians(mobile$device_lon)-as_radians(mobile$geofence_lon))
                   +sin(as_radians(mobile$device_lat))*sin(as_radians(mobile$geofence_lat)))

mobile$distance_squared = mobile$distance^2
mobile$ln_app_review_vol = log(mobile$app_review_vol)

```



# Descriptive Statistics

* 2a.	Summarize the data by calculating the summary statistics (i.e., mean, median, std. dev., minimum and maximum) for didclick, distance, imp_large, cat_entertainment, cat_social, cat_tech, os_ios, ln_app_review_vol and app_review_val.

```{r}
my_data <- as.data.frame(mobile[, c("didclick","distance","imp_large","cat_entertainment","cat_social","cat_tech","os_ios","ln_app_review_vol","app_review_val")])


stargazer(my_data, type="text", median=TRUE, digits=4, title="Summary Statistics")
```

* 2b.	Report the correlations among the above variables.

```{r}
res <- cor(my_data)
res
round(res, 4)
corrplot(res, method = "circle")

```

* 2c.	Plot the relationship of distance (x-axis) and click-through-rate (y-axis), and any other pairs of variables of interest. Bin the continuous "distance" into discrete "distance_group" where (0, 0.5] -->1, (0.5, 1] --> 2, (1, 2] --> 3, (2,4] -->4, (4, 7] --> 5, (7, 10] --> 6, >10 -->7.

```{r}
mobile$distance_group = ifelse(mobile$distance>0 & mobile$distance <= 0.5, 1,
                               ifelse(mobile$distance <= 1, 2,
                                      ifelse(mobile$distance <= 2, 3,
                                             ifelse(mobile$distance <= 4, 4,
                                                    ifelse(mobile$distance <= 7, 5,
                                                           ifelse(mobile$distance <=10, 6, 7))))))

impressions = ddply(mobile, c("distance_group"), summarise, nrows = length(distance_group))

didclick_group = aggregate(mobile$didclick, by=list(distance_group=mobile$distance_group), FUN=sum)


clickthrough  = merge(impressions, didclick_group, by = "distance_group")
clickthrough$ctr = clickthrough$x / clickthrough$nrows
clickthrough

plot(clickthrough$distance_group,clickthrough$ctr)

```



# Logistics Regression

* a.	Specify the following Logistic regression model:
Dependent variable: didclick; 
Independent variables: distance, distance_squared, imp_large, cat_entertainment, cat_social, cat_tech, os_ios, ln_app_review_vol and app_review_val.

Create a new data frame including all predictors.

```{r}
mobile2 <- as.data.frame(mobile[,c("didclick", "distance", "distance_squared", "imp_large", "cat_entertainment",
                                   "cat_social", "cat_tech", "os_ios", "ln_app_review_vol", "app_review_val")])

```

Before fitting into the logistic regression model, let's see the correlation between the predictors.

```{r}
res2 <- cor(mobile2)
res2
round(res2, 4)

corrplot(res2, method = "circle")
```

* b.	Estimate the model in R (using the glm function) and report coefficients and p-value of the estimates.

```{r}
reg1 <- glm(didclick ~ distance + distance_squared + imp_large + cat_entertainment
                   + cat_social + cat_tech + os_ios + ln_app_review_vol + app_review_val,
                   data = mobile2, family = binomial())

summary(reg1)
```

Some of the variables are insignificant, let's try adding some interaction terms.

```{r}
reg2 <- glm(didclick ~ log(distance) + distance_squared + imp_large + cat_entertainment + app_review_val*cat_entertainment
            + cat_social + cat_social*app_review_val +  cat_tech*imp_large + os_ios  
            + app_review_val*os_ios + ln_app_review_vol  + app_review_val
            + distance*ln_app_review_vol + distance_squared*ln_app_review_vol,
            data = mobile2, family = binomial())
summary(reg2)

```

We can see model 2 has a lower AIC score, which means it's an imoroved model.
We can also calculate the McFadden's Pseudo R-squared for the two models.

```{r}
nullmod1 <- glm(didclick~1, data  = mobile2, family="binomial")
1-logLik(reg1)/logLik(nullmod1)

nullmod2 <- glm(didclick~1, data  = mobile2, family="binomial")
1-logLik(reg2)/logLik(nullmod2)
```

* Diagnostic test for logistic regression 

step 1: residual plot

```{r}
plot(predict(reg1, type="response"),
             residuals(reg1, type= "deviance"))

plot(predict(reg2, type="response"),
             residuals(reg2, type= "deviance"))
```

step 2: influential plots

```{r}
plot(hatvalues(reg1)) 
plot(rstudent(reg1)) 
plot(cooks.distance(reg1))

plot(hatvalues(reg2)) 
plot(rstudent(reg2)) 
plot(cooks.distance(reg2))
```

step 3:  overdispersion

The expected variance for data drawn from a binomial distribution is σ2 = nπ(1 − π), where n is the number of observations and π is the probability of belonging to the Y = 1 group. Overdispersion occurs when the observed variance of the response variable is larger than what would be expected from a binomial distribution. Overdispersion can lead to distorted test standard errors and inaccurate tests of significance.

One way to detect overdispersion is to compare the residual deviance with the
residual degrees of freedom in your binomial model. 
If the ratio is considerably larger than 1, you have evidence of overdispersion. Applying this to the mobile example, I have

```{r}
deviance(reg2)/df.residual(reg2)
```
With logistic regression, overdispersion is suggested if the ratio of the residual deviance to the residual degrees of freedom is much larger than 1, which is not our case here.

We will choose the second model as the final model.

Recall:
```{r, echo=FALSE}
reg2 <- glm(didclick ~ log(distance) + distance_squared + imp_large + cat_entertainment + app_review_val*cat_entertainment
            + cat_social + cat_social*app_review_val +  cat_tech*imp_large + os_ios  
            + app_review_val*os_ios + ln_app_review_vol  + app_review_val
            + distance*ln_app_review_vol + distance_squared*ln_app_review_vol,
            data = mobile2, family = binomial())
summary(reg2)

```

By looking at p-value, except for log(distance), all other variables, including the intercept, are significant.
app_review_val, os_ios, app_review_val:os_ios, imp_large, distance:ln_app_review_vol are the most important ones.
Let’s look at the regression coefficients:
```{r}
coef(reg2)

```

In a logistic regression, the response being modeled is the log(odds) that Y = 1. The regression coefficients give the change in log(odds) in the response for a unit change in the predictor variable, holding all other predictor variables constant.
Because log(odds) are difficult to interpret, we can exponentiate them to put the results on an odds scale:

```{r}
exp(coef(reg2))

```

Now we can see that the odds of an impression click are decreased by a factor of -1.146428 if the imp_size="728x90",  (holding other variables constant). Conversely, the odds of an impression click are multiplied by a factor of 3.177699e-01 for imp_size="728x90". 

The odds of an impression click increase with log(distance), cat_social, cat_tech, ln_app_review_vol, imp_large:cat_tech, app_review_val:os_ios, distance_squared:ln_app_review_vol, and decrease with distance_squared, imp_large, cat_entertainment, app_review_val, os_ios, app_review_val:cat_social and distance:ln_app_review_vol. 

The interaction terms such as app_review_val:os_ios, means the relationship  bewteen app_review_val and whether a user clicked the impression, depending on whether the user is using an ios device or not.

When the predictor variables all equal 0, the intercept in this case means when imp_size not equal "728x90", app_topcat not euql "IAB1", "IAB1-6", "IAB14", or "IAB19-6", and the user is not using an ios device, the odds of an impression click are decreased by a factor of -4.13447269, or Conversely, the odds of an impression click are multiplied by a factor of 1.601111e-02.


* c. Findings and their implications

Users tend to click on impressions higher in app_review_val and choose establishments that are closer to them
Categories of the app is  important.
Impression size matters.
ios users on average are less likely to click. However, they are more likely to click if the app has higher star rating.
App review volume matters.
For a click decision, distance is not significant.

